Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-21 paper/main.tex
added description of exploratory correlation analysis

\subsubsection*{Comparing recent versus baseline measurements.}
We were interested in separating out potential associations between
\textit{absolute} fitness metrics and \textit{relative} metrics.  To
this end, in addition to assessing potential raw
(absolute) fitness metrics, we also defined a simple measure of recent
changes in those metrics, relative to a baseline.  We

In order to study

\subsubsection*{Exploratory correlation analyses}
\paragraph*{Imputation and interpolation of missing data.}

>>>>

\subsubsection*{Comparing recent versus baseline measurements.}
We were interested in separating out potential associations between
\textit{absolute} fitness metrics and \textit{relative} metrics.  To
this end, in addition to assessing potential raw
(absolute) fitness metrics, we also defined a simple measure of recent
changes in those metrics, relative to a baseline:
\[
  \Delta_{R, B} m = \frac{\frac{1}{R} \sum_{i = 1}^R
  m(i)}{\frac{1}{B} \sum_{i=R + 1}^{R+B}m(i)},
\]
where $m(i)$ is the value of metric $m$ from $i - 1$ days prior to testing (e.g.,
$m(1)$ represents the value of $m$ on the day the participant accepted
the HIT, and $m(10)$ represents the value of $m$ 9 days prior to
accepting the HIT.  Unless otherwise noted, we set $R = 7$ and $B =
30$.  In other words, to estimate recent changes in any metric $m$, we
divided the average value of $m$ taken over the prior week by the
average value of $m$ taken over the 30 days before that.

\subsubsection*{Exploratory correlation analyses}
We used a bootsrap procedure to identify reliable correlations between
different memory-related, fitness-related, and demographic-related
variables.  For each of $N = 1000$ iterations, we selected (with
replacement) a sample of 113 participants to include.  This yielded,
for each iteration, a sampled ``data matrix'' with one row per sampled
participant and one column for each measured variable.  When
participants were sampled multiple times in a given iteration, as was
often the case, this matrix contained duplicate rows.  We used a
round-robin imputation procedure to estimate the values of any missing
features~\citep{Buck60}.  Next, we computed the Pearson's correlation
between each pair of columns.  This yielded, for each pair of columns,
a distribution of $N$ bootstrapped correlation coefficients.  If fewer
than $95\%$ of the coefficients for a given pair of columns had the
same sign, we excluded the pair from further analysis and considered
the expected correlation between those columns to be undefined.  If
$\geq 95\%$ of the coefficients for a given pair of columns had the
same sign, we computed the expected correlation coefficient as:
\[
  \mathbb{E}_{i, j}\left[ r\right] = \tanh\left(\frac{1}{N} \sum_{n=1}^N
  \tanh^{-1}(\mathrm{corr}\left(m(i)_n, m(j)_n\right))\right),
\]
where $m(x)_n$ represents column $x$ of the bootstrapped data matrix
for iteration $n$, $\tanh$ is the hyperbolic tangent, and $\tanh^{-1}$
is the inverse hyperbolic tangent.
